Understanding the Impact of Mortgage State and Income on Household Poverty Status

### 2024-04-02 paper/paper.qmd
fix data feature

1. h_seq: Household sequence number, unique identifier for each household.

2. spm_poor: the poverty status; 1 representing "In poverty" and 0 represneting "Not in poverty".

3. spm_tenmortstatus: household's tenure/mortgage status; 1 representing "Owner with Mortgage", 2 representing "Owner without Mortgage or rent-free", and 3 representing "Renter".

4. spm_totval: household's cash income, unit in USD.

5. spm_snapsub: Supplemental Nutrition Assistance Program (SNAP) subsidy, unit in USD.

6. spm_caphousesub: capped housing subsidy, unit in USD.

7. spm_schlunch: school lunch subsidy, unit in USD.

8. spm_engval: energy subsidy, unit in USD.

9. spm_wicval: Women, Infants, and Children subsidy, unit in USD.

10. spm_fedtax: Federal tax, unit in USD.

11. spm_eitc: Federal Earned Income Tax Credit, unit in USD.

12. spm_actc: Additional Child Tax Credit, unit in USD.

13. spm_fica: Federal Insurance Contributions Act and federal retirement contribution, unit in USD.

14. spm_sttax: state tax, unit in USD.

15. spm_childsuppd: child support paid, unit in USD.

16. spm_capwkccxpns: capped work and child care expense, unit in USD.

17. spm_medxpns: Medical Out-Of-Pocket (MOOP) and Medicare Part B subsidy, unit in USD.

@@

>>>>

@@

```{r}
#| label: tbl-feature
#| tbl-cap: "Preview of the raw 2019 US Supplemental Poverty Measure dataset"
#| message: false
#| echo: false
#| warning: false

# show data feature
feature <- tibble(
  Data_feature = c("h_seq", "spm_poor", "spm_tenmortstatus", "spm_totval", "spm_snapsub", "spm_caphousesub", "spm_schlunch", "spm_engval", "spm_wicval", "spm_fedtax", "spm_eitc", "spm_actc", "spm_fica", "spm_sttax", "spm_childsuppd", "spm_capwkccxpns", "spm_medxpns"),
  Data_definition = c("Household sequence number, unique identifier for each household.", "the poverty status; 1 representing 'in poverty' and 0 representing 'not in poverty'.", "household's tenure/mortgage status; 1 representing 'owner with Mortgage', 2 representing 'owner without Mortgage or rent-free', and 3 representing 'renter'.", "household's cash income, unit in USD.", "Supplemental Nutrition Assistance Program (SNAP) subsidy, unit in USD.", "capped housing subsidy, unit in USD.", "school lunch subsidy, unit in USD.", "energy subsidy, unit in USD.", "Women, Infants, and Children subsidy, unit in USD.", "Federal tax, unit in USD.", "Federal Earned Income Tax Credit, unit in USD.", "Additional Child Tax Credit, unit in USD.", "Federal Insurance Contributions Act and federal retirement contribution, unit in USD.", "state tax, unit in USD.", "child support paid, unit in USD.", "capped work and child care expense, unit in USD.", "Medical Out-Of-Pocket (MOOP) and Medicare Part B subsidy, unit in USD.")
)
kable(feature, "latex") %>%
  column_spec(2, width = "30em")
```
